%
% File: chap_1.tex
% Author: Yuil Tripathee
%
\chapter{Introduction}

\section{Background and Motivation}

As of 2024, we stand in the face of turbulent geopolitics, frequent extreme weather events, and escalating living cost all around the world. And we chose to make a small step today towards a greater impact tomorrow. Unreasonable consumer demands is believed to be one of the leading factors that is keeping us behind on our goal of developing sustainable societies and planet. UN SDG goal 12 promotes sustainable consumption and production patterns, ensuring efficient use of natural resources.

This inspired us to found G2U. We are developing on online e-commerce platform where every treasure has a find its second life, to a new owner. Finding the gap in this nascent niche market, we intend to incorporate lean startup model to gain market knowledge \& feedback to the maximum. Then, our agile engineering team will capitalize on the market input swiftly to capture the sizable market share.

% What value will customer gain? 1 5 10 20 yr )

% Big impacts comes from small steps together.

\section{Market study}

% TAM, SAM, SOM (starting out)

In global outlook,  the refurbished electronics market is projected to experience significant growth from \$48.29 billion in 2022 to \$94.10 billion by 2030, at a compound annual growth rate (CAGR) of 12\%. 

This highlights an expanding demand for more sustainable and affordable alternatives in electronics, driven by both economic and environmental causalities.

\subsection{SEA Market}

Here is the outline for SEA Market:

\begin{description}
	\item[Cultural Thriftiness:] Thai consumers have a strong inclination toward affordability, making value-for-money products highly popular.
	\item[Ecological Consciousness:] Over recent years, there has been a growing awareness among Thai consumers about sustainability. 
	\item[Affordability and Sustainability:] he twin goals of affordability and sustainability are guiding factors in the growing adoption of refurbished electronics in Thailand. 
\end{description}

\subsection{EU Market}

We see a different outlook in the EU market:

\begin{description}
	\item[Affordability in Tough Economic Times:]  The EU has seen economic pressures, especially in the wake of the COVID-19 pandemic and rising inflation caused by war in Ukraine.
	 \item[Eco-labeling and Tax Incentives: ] Some EU countries have introduced eco-labeling schemes for refurbished products, allowing consumers to easily identify environmentally friendly options.
	 \item[Repair and Reuse Policies: ]  The EU has also introduced policies that encourage the repair and reuse of electronic devices. The Right to Repair initiative, for example, aims to ensure that consumers can easily repair their products, thus extending their lifecycle and reducing the need for new purchases.
\end{description}

\section{Scope of work}

G2U is an innovative online platform designed to simplify the buying, selling, and donating of second-hand reusable items, with a strong focus on affordability and environmental sustainability. The platform differentiates itself from competitors like Lazada and Shopee by emphasizing eco-conscious practices and promoting a circular economy.

Concisely, we have segregated the scope of work into the following deliverables:

\begin{enumerate}
	\item Interactive online platform.
	\item Project documentation (diagrams, reports, presentation).
	\item Information gathered from user feedback.
\end{enumerate}

% fraction of the cost (what customer want to see)

% partnership Investment EUR 750,000, Equity 35%, ROI after 8 years 30%

% find a way to develop recurring customers -> giveaways platform

% commercializing the platform

% scaling model

% competitors, price market

% relationship focused marketing strategy (B2B) meetups

%\section{A dummy section}

% let's take a look at how G2U will be winning investment for you.

% after completing a successful pilot project, we are gearing up for significant expansion. Fueled by your investment, positioning us for rapid scale up. Laying the groundwork (spending your investment, )

% roadmap future road map

% it's a strategic move to gain projected revenue of 9M EUR after only 8 years of your investment

% G2U will begin making profit after 3 years RO Equity 30% (EPS), thanks to our incremental funding model maximizing revenue while minimizing operating cost.

% exit strategy after 10 years IPO -> shareholder value or strategic acquisition

%\begin{figure}[!h]
%	\centering
%	\begin{tikzpicture}
%		\Tree
%		[.A
%		[.B
%		\edge[]; {E}
%		\edge[]; {F}
%		\edge[]; {G}
%		]
%		[.C 
%		\edge[]; {H}
%		\edge[]; {I}
%		\edge[]; {J}
%		]
%		[.D 
%		\edge[]; {K}
%		\edge[]; {L}
%		\edge[]; {M}
%		]
%		]
%	\end{tikzpicture}
%	\caption{The proposed tree structure for the array implementation.}
%\end{figure}

\clearpage