%
% File: chap_6.tex
% Author: Yuil Tripathee
%
\chapter{Evaluation of Outcomes}

\section{Testing Methodologies}

So far, testing code correctness has been least of the issue. There we will continue performing higher level tests to confirm user's perception of our app. Here are the few methods we found appropriate:

\begin{description}
	\item[A/B Testing] We consider this as the most important test to retain user's feedback. If we give only one interface for user to test, users perceive this as an open ended questionnaire. It makes the participants in the test anxious and fall back to their previous experiences with the similar platform. But, if we provide the tester with two set of alternatives, it is quite easier to make comparative evaluation. Click up rate test compared in different applications helps us to exploit the things users are not willing to semantically express in the test participation (verbally or in written).
	\item[Integration Testing] Such tests allow testing multiple parts of the software system as the group. We perform this test to see if two modules are interfacing well together, as this is an internal test. This test sets an important precedence before we bring our platform for review with the external users.
	\item[Stress Testing] This is on the technical side and least relevant for now. Since our user base is small, this test has no use so far till now. But, in the coming future we might have to go through vertical and horizontal integration. We have to know how well the app can handle the load and where optimizations need to be made.
\end{description}

\section{Results}

We have observed A/B testing being tried and tested in by multiple tech companies. Facebook and YouTube gradually roll out their test features and set it as optional. Now, only thing left is to wait and watch user's behavior, especially which service do the users want to stay longer on. The classic example being Apple rolling their flagship MacBook Pro lineup with touch-bar and phasing it out after facing criticism.

We were able to replicate such methodologies my letting users make comparative evaluation between our previous MVP and iterative successor version of our platform. This test also blends with agile method which allows improvements in our platform with the least overhead. We have discovered this method to be the most effective in our test experience and it provides significantly better actionable information that lets the improvement of our application.

\clearpage