%
% File: chap_2.tex
% Author: Yuil Tripathee
%
\chapter{Project Management}
% Software Process Framework
% Covers the following modules:
% M1_2: software process frameworks overview
% M2_1: software process
% M2_2: agile software development

%\textit{TODO: Comparative analysis of each methodology and what they deliver}

\section{Incremental funding methodology}

We use this technique to delegate high level business decisions. Each improvements to app that involves cash flow has to go through internal rate of return test for that particular incremental investment.

We intend to utilize lean startup principles to minimize upfront investments, iterate quickly, and validate assumptions with real customer feedback. The main goal of this model is to develop a sustainable cash flow model for scaling. \cite{2024_Lean_Startup}

Instagram's acquisition by Facebook for \$1 billion with just 13 full-time employees highlights the potential for scalability and profitability with a lean team. Ad revenue benchmarks provide context for monetization strategies: \cite{2012_IG_Acquisition}

\begin{description}
	\item[CPC:] \$0.5–\$3.5
	\item[CPM:] \$2–\$20
	\item[SPE:] \$0.03–\$0.08
\end{description}

%\textit{Instagram acquisition story on 2012 on \$ 1 billion having 13 full time employees only. CPC from \$ 0.5 to \$ 3.5, CPM for \$ 2 to \$ 20 and SPE from \$ 0.03 to \$ 0.08.} \cite{2012_IG_Acquisition}

%\textit{TODO: Project management (lecture 1) -> define scope, timeline, budget.}

%\textit{TODO: Communication and Rationale Management.}

\section{Agile Method with Kanban Tool}

Our team decided to use a blend of Scrum and Kanban tactics under Agile methodology. So far, it has been rewarding to adapt with necessary changes. Going forward, we have continued to stay with this plan. The particular details around the project management are sufficiently provided in other formats of project submission.

\clearpage